19Q1

### 2019-04-30 19Q1.Rmd
updated Rmd

ggsave("./plots/manuscript/crispr_spearman_corr_plot.pdf", crispr_spearman_corr_plot, device = "pdf", dpi = 450, width = 20, height = 10, units = "in")
```

@@

Kolmogorov-Smirnov tests comparing DGLs that are in a G2P DGL and not.
```{r, eval=FALSE, fig.height=6, fig.width=12}
g2p_corr_all <- G2PCorrTable(ccle_ptmuts_df = ccle_ptmuts, ctrp_ptmuts_df = ctrp_ptmuts, gdsc_ptmuts_df = gdsc_ptmuts)
g2p_mut_stats <- G2PCorrStatsTables(corr_df = g2p_corr_all, table_type = "mutation")
g2p_corr_stats <- G2PCorrStatsTables(corr_df = g2p_corr_all, table_type = "KS")

g2p_corr_4plot <- g2p_corr_all
g2p_corr_4plot$p <- NULL
g2p_corr_4plot$Mut_Signif <- NULL
g2p_corr_4plot <- melt(g2p_corr_4plot, id.vars = colnames(g2p_corr_4plot)[1:5], measure.vars = colnames(g2p_corr_4plot)[6:7], value.name = "Correlation")
g2p_corr_4plot <- g2p_corr_4plot %>% separate(col = variable, into = c("Correlation_Method", "corr", "Metric"), sep = "_", remove = FALSE)
g2p_corr_4plot$Metric <- ifelse(g2p_corr_4plot$Metric == "GE", "Gene Expression", "Copy Number")

>>>>

# ggsave("./plots/manuscript/crispr_spearman_corr_plot.pdf", crispr_spearman_corr_plot, device = "pdf", dpi = 450, width = 20, height = 10, units = "in")
```

@@

Kolmogorov-Smirnov tests comparing DGLs that are in a G2P DGL and not.
```{r, eval=FALSE, fig.height=6, fig.width=12}
# g2p_corr_all <- G2PCorrTable(ccle_ptmuts_df = ccle_ptmuts, ctrp_ptmuts_df = ctrp_ptmuts, gdsc_ptmuts_df = gdsc_ptmuts)
# saveRDS(g2p_corr_all, "./data_munging/rds/g2p_corr_all.rds")
g2p_corr_all <- readRDS("./data_munging/rds/g2p_corr_all.rds")
g2p_mut_stats <- G2PCorrStatsTables(corr_df = g2p_corr_all, table_type = "mutation")
g2p_corr_stats <- G2PCorrStatsTables(corr_df = g2p_corr_all, table_type = "KS")

g2p_corr_4plot <- g2p_corr_all
g2p_corr_4plot$p <- NULL
g2p_corr_4plot$Mut_Signif <- NULL
g2p_corr_4plot <- melt(g2p_corr_4plot, id.vars = colnames(g2p_corr_4plot)[1:6], measure.vars = colnames(g2p_corr_4plot)[7:8], value.name = "Correlation")
g2p_corr_4plot <- g2p_corr_4plot %>% separate(col = variable, into = c("Correlation_Method", "corr", "Metric"), sep = "_", remove = FALSE)
g2p_corr_4plot$Metric <- ifelse(g2p_corr_4plot$Metric == "GE", "Gene Expression", "Copy Number")
